---
title: "Set up connection to surveys"
output: html_notebook
---

```{r, echo=FALSE}
knitr::opts_chunk$set(eval=FALSE)
```

This is the 'instructions' version of the code. The file that is actually run is `connect_API.R`.

## 1. Install the required packages

The `surveymonkey` package makes it easier to access the Survey Monkey API in R. It is developed and maintained by TNTP, a nonprofit company working to end the injustice of educational inequality.

```{r, eval}
# for wrangling, viz, etc.
if(!require("tidyverse")) {
  install.packages("tidyverse")
}

# easy editting of R environments
if(!require("usethis")) {
  install.packages("usethis")
}

# Need devtools install surveymonkey package from github
if(!require("devtools")) {
  install.packages("devtools")
}

# Get the dev version of surveymonkey package 
# https://github.com/tntp/surveymonkey
devtools::install_github("tntp/surveymonkey")

```

```{r}
library("surveymonkey")
library("tidyverse")
```

## 2. Set up an API key in Survey Monkey

At time of writing, you create your access token by making a new private app here: https://developer.surveymonkey.com/apps/.

Then follow these intructions from the surveymonkey package documentation (or more updated authentication information):

Add the SurveyMonkey account’s OAuth token to your .Rprofile file. To open and edit that file, run `usethis::edit_r_profile()`, then add a line like this: `options(sm_oauth_token = "kmda332fkdlakfld8am7ml3dafka-dafknalkfmalkfad-THIS IS NOT THE REAL KEY THOUGH").`

WARNING 1: Don't share the token or accidentally add it on GitHub, etc.

WARNING 2: Pay attention to the number of requests you are allowed to make in a day. At time of writing, 500.

WARNING 3: Only 100 responses can be fetched per API call, a survey with X respondents will make at least X/100 calls to the API.

```{r}
# Get the latest 10 (or n) surveys so you can find the IDs for the surveys you want
surveys <- browse_surveys(10)
```
## 3. Get the data

Here I'm saving the data as .csv that can be used as back up and more easily integrated into the site.

```{r}
# This took 6 requests when last run
grads_raw <- 302886746 %>% 
  fetch_survey_obj %>%
  parse_survey
```

```{r}
grads_min <- grads_raw %>% 
  # Say that a submission is complete if they answered up to the disability question
  # This increased the number of completes slightly. Should be checked in final processing.
  mutate(complete = !is.na(`Do you identify as a person with a disability?`)) %>% 
  select(date_modified, response_status, 
         `Please tell us the organisation you joined as a graduate.`,
         complete) %>% 
  rename(Employer = `Please tell us the organisation you joined as a graduate.`) 

write_csv(grads_min, str_c("Data/fromAPI/", Sys.time(), "_grads.csv"))
```

```{r}
# This took 3 requests when last run
interns_raw <- 302886733 %>% 
  fetch_survey_obj %>%
  parse_survey
```

```{r}
interns_min <- interns_raw %>% 
  # Say that a submission is complete if they answered up to the disability question
  # This increased the number of completes slightly. Should be checked in final processing.
  mutate(complete = !is.na(`Do you identify as a person with a disability?`)) %>% 
  select(date_modified, response_status, 
         `With which organisation did you undertake your most recent internship?`,
         complete) %>% 
  rename(Employer = `With which organisation did you undertake your most recent internship?`) 

write_csv(interns_min, str_c("Data/fromAPI/", Sys.time(), "_interns.csv"))
```

```{r}
# This took 2 requests when last run
employers_raw <- 302886711 %>% 
  fetch_survey_obj %>%
  parse_survey
```


```{r}
employers_min <- employers_raw %>% 
  # Say that a submission is complete if they answered up to the disability question
  # This increased the number of completes slightly. Should be checked in final processing.
  mutate(complete = !is.na(`What challenges does your organisation face in transitioning graduates from their graduate programme to non-graduate roles, if any?`)) %>% 
  select(date_modified, response_status, 
         `What is the name of your organisation?`,
         complete) %>% 
  rename(Employer = `What is the name of your organisation?`) 

write_csv(employers_min, str_c("Data/fromAPI/", Sys.time(), "_employers.csv"))
```
