---
title: "Dashboard 2021"
description: |
 Status of responses for the NZAGE graduate, intern and employer surveys. Updated at least daily.
site: distill::distill_website
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
---

```{r, eval = FALSE, echo=FALSE}
# Packages needed. Should only have to run once
list_of_packages <- c("tidyverse", "lubridate", "fuzzyjoin", "plotly",
                      "DT", "knitr", "widgetframe")
to_install <- list_of_packages[!(list_of_packages %in% installed.packages()[,"Package"])]
if(length(to_install)) install.packages(to_install)
```
```{r libraries, include=FALSE}
library(tidyverse)
library(lubridate)
library(fuzzyjoin)
library(DT)
library(widgetframe)
library(knitr)
library(plotly)


knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, error=FALSE)
mycol = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f')
mycol2 <- c("#550D80", "#EDA82F", "#299E73")
```
```{r}
# Concordance
# Tip: I was getting some weird space characters from the CSV 
# that showed up as question marks in diamonds in Viewer. 
# Did a replace all spaces with spaces in the .csv. Worked.

ref = read_csv("Data/org-ref.csv") %>% 
  rename(org_messy = Organisation) %>% 
  rename(Employer = `Correct Title`) %>% 
  select(1:3) %>% 
  filter(!is.na(Employer)) %>% 
  distinct()

employers <- ref %>% 
  select(Employer, Industry) %>% 
  distinct()

```
```{r}
# Read in the most recent saved files
files <- file.info(list.files("Data/fromAPI", full.names = T)) %>% 
  rownames_to_column("file_name") %>% 
  separate(file_name, sep = "_", into = c("date", "group"), remove = FALSE) %>% 
  # trim off the .csv
  mutate(group = str_remove(group, ".csv")) %>% 
  group_by(group) %>% 
  arrange(desc(mtime)) %>% 
  slice(1)
```
```{r}
# This currently implements two joins, one of known ways that people enter their company name and an additional fuzzy match
# This won't be perfect! List should be verified by a human somewhat regularly. 

grads_min <- read_csv(as.character(files[which(files$group == "grads"),1]))

grads_clean <- grads_min %>% 
  rowid_to_column() %>% 
  left_join(ref, by = c("Employer" = "org_messy"), suffix = c("", "_conc")) %>% 
  fuzzyjoin::stringdist_left_join(employers, max_dist = 5, 
                                  by = c("Employer" = "Employer"), 
                                  ignore_case = TRUE, distance_col = "diff") %>% 
  group_by(rowid) %>% 
  arrange(diff) %>% 
  slice(1) %>% 
  mutate(Employer = case_when(!is.na(Employer_conc) ~ Employer_conc, 
                              !is.na(Employer.y) ~ Employer.y,
                              TRUE ~ "Unknown")) %>% 
  filter(Employer != "Unknown")
```
```{r eval=FALSE}
# make a file to check
write_csv(filter(grads_clean, is.na(Employer_conc)), "Data/grad_issues.csv")
```
```{r}
# This currently implements two joins, one of known ways that people enter their company name and an additional fuzzy match
# This won't be perfect! List should be verified by a human somewhat regularly. 

interns_min <- read_csv(as.character(files[which(files$group == "interns"),1]))

interns_clean <- interns_min %>% 
  rowid_to_column() %>% 
  left_join(ref, by = c("Employer" = "org_messy"), suffix = c("", "_conc")) %>% 
  fuzzyjoin::stringdist_left_join(employers, max_dist = 5, 
                                  by = c("Employer" = "Employer"), 
                                  ignore_case = TRUE, distance_col = "diff") %>% 
  group_by(rowid) %>% 
  arrange(diff) %>% 
  slice(1) %>% 
  mutate(Employer = case_when(!is.na(Employer_conc) ~ Employer_conc, 
                              !is.na(Employer.y) ~ Employer.y,
                              TRUE ~ "Unknown")) %>% 
  filter(Employer != "Unknown")
```
```{r eval=FALSE}
# make a file to check
write_csv(filter(interns_clean, is.na(Employer_conc)), "Data/interns_issues.csv")
````
```{r}
employers_clean <- read_csv(as.character(files[which(files$group == "employers"),1])) %>% 
  rowid_to_column() %>% 
  left_join(ref, by = c("Employer" = "org_messy"), suffix = c("", "_conc")) %>% 
  fuzzyjoin::stringdist_left_join(employers, max_dist = 5, 
                                  by = c("Employer" = "Employer"), 
                                  ignore_case = TRUE, distance_col = "diff") %>% 
  group_by(rowid) %>% 
  arrange(diff) %>% 
  slice(1) %>% 
  mutate(Employer = case_when(!is.na(Employer_conc) ~ Employer_conc, 
                              !is.na(Employer.y) ~ Employer.y,
                              TRUE ~ "Unknown")) %>% 
  filter(Employer != "Unknown")
```
```{r}
### Set update time
update_time <- lubridate::with_tz(Sys.time(), tzone = "Pacific/Auckland")
update_time = format(update_time,format='%Y-%m-%d %H:%M')

```
_Last updated `r update_time`._

## Progress to date

The below charts track **complete** graduate, intern and employer surveys, as well as how many bespoke reports have been earned. The surveys close on September 10. 

#### Note on bespoke reports
An organisation earns a graduate or intern bespoke report when 10 or more of their graduates or interns, respecitvely, complete the survey. They must also be a member of the NZAGE—this update data only reflects whether they have 10 or more complete responses for the survey. Double check NZAGE status before confirming with an organisation.

### Complete responses to date compared with historical counts

```{r, fig.height=7}
# Historical data
historical_data <- tibble::tribble(
  ~Year,           ~Employers, ~Grads, ~Interns, ~`Grad bespoke reports`, ~`Intern bespoke reports`,
  "2018",             38L,            591L,           NA, 27, 0,
  "2019",             43L,            665L,         223, 27, 0, 
  "2020",             48L,            863L,         320, 44, 37, 
  ) %>% 
  pivot_longer(-Year, names_to = "type", values_to = "n" )


# Count bespokes
bespokes <- grads_clean %>% 
  filter(complete) %>% 
  group_by(Employer) %>% 
  count() %>% 
  filter(n >= 10)

intern_bespokes <- interns_clean %>% 
  filter(complete) %>% 
  group_by(Employer) %>% 
  count() %>% 
  filter(n >= 10)
  
# Stack all the data
full <- bind_rows(list(Employers = employers_clean, Grads = grads_clean, Interns = interns_clean), .id = "type") %>% 
  select(type, Employer, date_modified, complete) %>% 
  filter(complete)

summary <- full %>% 
  group_by(type) %>% 
  count() %>% 
  bind_rows(tibble(type = "Grad bespoke reports", n = nrow(bespokes))) %>% 
  bind_rows(tibble(type = "Intern bespoke reports", n = nrow(intern_bespokes))) %>% 
  mutate(Year = "YTD") %>% 
  bind_rows(historical_data) %>% 
  rename(Count = n) %>% 
  mutate(type = factor(type, levels = c("Grads", "Grad bespoke reports", "Interns", "Intern bespoke reports", "Employers")))

summary %>% 
  ggplot(aes(x = Year, y = Count, fill = as.factor(Year))) +
  geom_bar(stat = "identity") +
  facet_wrap(~type, scales = "free_y", nrow = 3) +
  theme_minimal() +
  geom_text(aes(label = Count), vjust = -0.3) +
  theme(panel.grid=element_blank()) +
  geom_blank(aes(y=Count*1.2)) +
  theme(strip.text.x = element_text(size = 12)) +
  guides(fill=FALSE) +
  scale_fill_manual(values=mycol[c(1,2,3,5)]) +
  #ggtitle("Complete responses to date compared with historical counts") +
  labs(caption = "Prepared by Talent Solutions for the NZAGE, 2021")

```

### Cumulative complete responses over time for 2021 surveys

The solid lines below represent the current cumulative responses to all three surveys. The dotted lines and final diamond points indicate the path to equalling last year's final numbers by the set survey closing date.

```{r, fig.height=5}
survey_close = lubridate::ymd("2021-09-10")
alt_hist = filter(historical_data, Year == "2020") %>% 
  filter(type != "Grad bespoke reports") %>% 
  filter(type != "Intern bespoke reports") %>% 
  rename(alt_n = "n") %>% 
  mutate(myx = survey_close)

end_point_assistant <- tibble(type = c("Employers", "Interns", "Grads"),
                              Date = max(lubridate::ymd(as.Date(full$date_modified))))

linegraph_data <- full %>% 
  mutate(Date = lubridate::ymd(as.Date(date_modified))) %>% 
  group_by(type, Date) %>% 
  count() %>% 
  group_by(type) %>% 
  mutate(`Cumulative count` = cumsum(n)) %>% 
  group_by(type) %>% 
  bind_rows(end_point_assistant) %>% 
  arrange(type, Date) %>% 
  fill(`Cumulative count`)

coords <- linegraph_data %>% 
  filter(Date == max(Date)) %>% 
  left_join(alt_hist, by = "type") %>% 
  mutate(diff_date = parse_number(as.character(difftime(myx, Date)))) %>% 
  mutate(slope = (alt_n-n)/diff_date)
  

linegraph <- linegraph_data %>% 
  ggplot(aes(x = Date, y = `Cumulative count`, group = type, colour = type)) +
  geom_line() +
  geom_line(size=1.5) +
  geom_vline(aes(xintercept = survey_close), lty = 2) +
  geom_point(data = alt_hist, aes(x = myx, y = alt_n), pch = 18) +
  geom_segment(data = coords, aes(x = Date, y = `Cumulative count`, xend = myx, yend = alt_n), lty = 3) +
  theme_minimal() +
  theme(panel.grid.minor=element_blank()) +
  #ggtitle("Cumulative complete responses over time for 2021 surveys") +
  #facet_wrap(~type, ncol = 1, scales = "free") +
  theme(legend.position="bottom") +
  labs(colour = "") +
  scale_color_manual(values=mycol2) +
  labs(caption = "Prepared by Talent Solutions for the NZAGE, 2021") 

plotly::ggplotly(linegraph, tooltip = c("Date", "Cumulative count")) %>% 
    layout(legend = list(
      orientation = "h"
    )
  )

```

## Summary by organisation

```{r}

org_summary <- full %>% 
  group_by(Employer, type) %>% 
  count() %>% 
  ungroup() %>% 
  complete(Employer, type, fill = list(n = 0)) %>% 
  pivot_wider(id_cols = Employer, names_from = type, values_from = n) %>% 
  rename(`Complete Employer Survey?` = Employers) %>% 
  mutate(`Complete Employer Survey?` = if_else(`Complete Employer Survey?` > 0, "Yes", "No")) %>% 
  mutate(`Grad bespoke report?` = if_else(Grads >= 10, "Yes", "No")) %>% 
  mutate(`Intern bespoke report?` = if_else(Interns >= 10, "Yes", "No")) %>% 
  select(Employer, `Complete Employer Survey?`, Grads, `Grad bespoke report?`, Interns, `Intern bespoke report?`)

```

This sortable and searchable table shows all organisations that have had graduate, intern and/or employer responses in 2021. Only complete counts^[We have used a two-stage automated checking approach based on historical response patterns and 'fuzzy' matching to maximise correct coding of the free text responses that grads/interns provide to identify their employer. This coding will be human verified with final data cleaning and so these counts are subject to change as unidentified or misidentified employers are corrected.] are included.

`r DT::datatable(org_summary, rownames=FALSE)`

