---
title: "Dashboard 2021"
description: |
 Status of responses for the NZAGE graduate, intern and employer surveys. Updated at least daily.
site: distill::distill_website
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
---

```{r, eval = FALSE, echo=FALSE}
# Packages needed. Should only have to run once
list_of_packages <- c("tidyverse", "lubridate", "fuzzyjoin", "plotly",
                      "DT", "knitr", "widgetframe")
to_install <- list_of_packages[!(list_of_packages %in% installed.packages()[,"Package"])]
if(length(to_install)) install.packages(to_install)
```
```{r libraries, include=FALSE}
library(tidyverse)
library(lubridate)
library(fuzzyjoin)
library(DT)
library(widgetframe)
library(knitr)
library(plotly)


knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, error=FALSE)
mycol = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f')
```
```{r}
# Concordance
# Tip: I was getting some weird space characters from the CSV 
# that showed up as question marks in diamonds in Viewer. 
# Did a replace all spaces with spaces in the .csv. Worked.

ref = read_csv("Data/org-ref.csv") %>% 
  rename(org_messy = Organisation) %>% 
  rename(Employer = `Correct Title`) %>% 
  select(1:3) %>% 
  filter(!is.na(Employer)) %>% 
  distinct()

employers <- ref %>% 
  select(Employer, Industry) %>% 
  distinct()

```
```{r, eval = FALSE}
## To do

- Get the historical data
- Set up API to connect with Survey Monkey
- Set up CRON job to do updates
  - GitHub connection
- Check n for bespokes
- Fix email (optional)
- Add a URL if Seren wants (optional)


To ask for
- Historical bespokes counts?
- Threshold for bespokes still the same (10)?
```
```{r}
# Read in the most recent saved files
files <- file.info(list.files("Data/fromAPI", full.names = T)) %>% 
  rownames_to_column("file_name") %>% 
  separate(file_name, sep = "_", into = c("date", "group"), remove = FALSE) %>% 
  # trim off the .csv
  mutate(group = str_remove(group, ".csv")) %>% 
  group_by(group) %>% 
  arrange(desc(mtime)) %>% 
  slice(1)
```
```{r}
# This currently implements two joins, one of known ways that people enter their company name and an additional fuzzy match
# This won't be perfect! List should be verified by a human somewhat regularly. 

grads_min <- read_csv(as.character(files[which(files$group == "grads"),1]))

grads_clean <- grads_min %>% 
  rowid_to_column() %>% 
  left_join(ref, by = c("Employer" = "org_messy"), suffix = c("", "_conc")) %>% 
  fuzzyjoin::stringdist_left_join(employers, max_dist = 5, 
                                  by = c("Employer" = "Employer"), 
                                  ignore_case = TRUE, distance_col = "diff") %>% 
  group_by(rowid) %>% 
  arrange(diff) %>% 
  slice(1) %>% 
  mutate(Employer = case_when(!is.na(Employer_conc) ~ Employer_conc, 
                              !is.na(Employer.y) ~ Employer.y,
                              TRUE ~ "Unknown")) %>% 
  filter(Employer != "Unknown")
```
```{r eval=FALSE}
# make a file to check
write_csv(filter(grads_clean, is.na(Employer_conc)), "Data/grad_issues.csv")
````
```{r}
# This currently implements two joins, one of known ways that people enter their company name and an additional fuzzy match
# This won't be perfect! List should be verified by a human somewhat regularly. 

interns_min <- read_csv(as.character(files[which(files$group == "interns"),1]))

interns_clean <- interns_min %>% 
  rowid_to_column() %>% 
  left_join(ref, by = c("Employer" = "org_messy"), suffix = c("", "_conc")) %>% 
  fuzzyjoin::stringdist_left_join(employers, max_dist = 5, 
                                  by = c("Employer" = "Employer"), 
                                  ignore_case = TRUE, distance_col = "diff") %>% 
  group_by(rowid) %>% 
  arrange(diff) %>% 
  slice(1) %>% 
  mutate(Employer = case_when(!is.na(Employer_conc) ~ Employer_conc, 
                              !is.na(Employer.y) ~ Employer.y,
                              TRUE ~ "Unknown")) %>% 
  filter(Employer != "Unknown")
```
```{r eval=FALSE}
# make a file to check
write_csv(filter(interns_clean, is.na(Employer_conc)), "Data/interns_issues.csv")
````
```{r}
employers_clean <- read_csv(as.character(files[which(files$group == "employers"),1])) %>% 
  rowid_to_column() %>% 
  left_join(ref, by = c("Employer" = "org_messy"), suffix = c("", "_conc")) %>% 
  fuzzyjoin::stringdist_left_join(employers, max_dist = 5, 
                                  by = c("Employer" = "Employer"), 
                                  ignore_case = TRUE, distance_col = "diff") %>% 
  group_by(rowid) %>% 
  arrange(diff) %>% 
  slice(1) %>% 
  mutate(Employer = case_when(!is.na(Employer_conc) ~ Employer_conc, 
                              !is.na(Employer.y) ~ Employer.y,
                              TRUE ~ "Unknown")) %>% 
  filter(Employer != "Unknown")
```
```{r}
### Set update time
update_time <- lubridate::with_tz(Sys.time(), tzone = "Pacific/Auckland")
update_time = format(update_time,format='%Y-%m-%d %H:%M')

```
_Last updated `r update_time`._

## Progress to date

The below charts track **complete** graduate, intern and employer surveys, as well as how many bespoke reports have been earned. 

#### Note on bespoke reports
An organisation earns a bespoke report when 10 or more of their graduates complete the graduate survey. They must also be a member of the NZAGE—this update data only reflects whether they have 10 or more complete graduate response. Double check NZAGE status before confirming with an organisation.


```{r}
# Historical data
historical_data <- tibble::tribble(
  ~Year,           ~Employers, ~Grads, ~Interns, ~Bespokes,
  "2018",             38L,            591L,           NA, 27,
  "2019",             43L,            665L,         223, 27,
  "2020",             48L,            863L,         320, 25,
  ) %>% 
  pivot_longer(-Year, names_to = "type", values_to = "n" )


# Count bespokes
bespokes <- grads_clean %>% 
  filter(complete) %>% 
  group_by(Employer) %>% 
  count() %>% 
  filter(n >= 10)
  
# Stack all the data
full <- bind_rows(list(Employers = employers_clean, Grads = grads_clean, Interns = interns_clean), .id = "type") %>% 
  select(type, Employer, date_modified, complete) %>% 
  filter(complete)

summary <- full %>% 
  group_by(type) %>% 
  count() %>% 
  bind_rows(tibble(type = "Bespokes", n = nrow(bespokes))) %>% 
  mutate(Year = "YTD") %>% 
  bind_rows(historical_data) %>% 
  rename(Count = n) %>% 
  mutate(type = factor(type, levels = c("Grads", "Interns", "Employers", "Bespokes")))

summary %>% 
  ggplot(aes(x = Year, y = Count, fill = as.factor(Year))) +
  geom_bar(stat = "identity") +
  facet_wrap(~type, scales = "free_y") +
  theme_minimal() +
  geom_text(aes(label = Count), vjust = -0.3) +
  theme(panel.grid=element_blank()) +
  geom_blank(aes(y=Count*1.2)) +
  theme(strip.text.x = element_text(size = 12)) +
  guides(fill=FALSE) +
  scale_fill_manual(values=mycol[c(1,2,3,5)]) +
  ggtitle("Complete responses to date compared with historical counts") +
  labs(caption = "Prepared by Talent Solutions for the NZAGE, 2021")

```


```{r}
linegraph <- full %>% 
  mutate(Date = lubridate::ymd(as.Date(date_modified))) %>% 
  group_by(type, Date) %>% 
  count() %>% 
  group_by(type) %>% 
  mutate(`Cumulative count` = cumsum(n)) %>% 
  ggplot(aes(x = Date, y = `Cumulative count`, group = type, colour = type)) +
  geom_line() +
  geom_line(size=1.5) +
  theme_minimal() +
  theme(panel.grid.minor=element_blank()) +
  ggtitle("Cumulative complete responses over time for 2021 surveys") +
  #facet_wrap(~type, ncol = 1, scales = "free") +
  theme(legend.position="bottom") +
  labs(colour = "") +
  scale_color_manual(values=mycol[c(2,3,5)]) +
  labs(caption = "Prepared by Talent Solutions for the NZAGE, 2021") 

plotly::ggplotly(linegraph, tooltip = c("Date", "Cumulative count")) %>% 
    layout(legend = list(
      orientation = "h"
    )
  )

```

## Summary by organisation

```{r}

org_summary <- full %>% 
  group_by(Employer, type) %>% 
  count() %>% 
  ungroup() %>% 
  complete(Employer, type, fill = list(n = 0)) %>% 
  pivot_wider(id_cols = Employer, names_from = type, values_from = n) %>% 
  rename(`Complete Employer Survey?` = Employers) %>% 
  mutate(`Complete Employer Survey?` = if_else(`Complete Employer Survey?` > 0, "Yes", "No")) %>% 
  mutate(`Bespoke report?` = if_else(Grads >= 10, "Yes", "No")) %>% 
  select(everything(), Grads, `Bespoke report?`)

```

This sortable and searchable table shows all organisations that have had graduate, intern and/or employer responses in 2021. Only complete counts^[While we have used a two-stage automated checking approach to maximise correct coding of free text responses identifying the employer of each graduate and intern, these numbers may change somewhat with final data cleaning as unidentified or misidentified employers are corrected.] are included.

`r DT::datatable(org_summary)`

